---
title: "Title"
author: "Authors"
date: "`r Sys.Date()`"
output: 
  word_document:
    # Template styles in word
    reference_docx: template.docx
    # Add this exe in the pandoc folder to manage cross references
    pandoc_args: ["-Fpandoc-crossref"]
bibliography: Library.bib
csl: international-journal-of-digital-earth.csl
editor_options: 
  markdown: 
    wrap: 72
---

---
figureTitle: "Figure"
tableTitle: "Table"
equationTitle: "Equation"
eqnPrefix: "equation"
figPrefix: 
  - "fig."
  - "figs."
---

```{r setup, echo = FALSE, message=FALSE, warning=FALSE, results='hide'}
library(tidyverse)
library(lemon)
library(flextable)
library(magick)
library(grid)

# Load data
df <- read.csv("mydata.csv")

# Flextable options
set_flextable_defaults(
  font.family = "Times New Roman",
  font.size = 12, 
  theme_fun = function(x) theme_booktabs(x,bold_header = TRUE),
  padding = 6,
  background.color = "#FFFFFF",
  digits = 2,
  decimal.mark = ".",
  big.mark = ",",
  na_str = "-")

knitr::knit_hooks$set(crop = knitr::hook_pdfcrop)

# Auto figure and table number
figure_f = local({
  i = 0
  function(x) {
    i <<- i + 1
    paste('Figure ', i, '. ', x, sep = '')
  }
})

table_f = local({
  j = 0
  function(x) {
    j <<- j + 1
    paste('Table ', j, '. ', x, sep = '')
  }
})
```

# Introduction

Here is my intro, references separated by ; [@Solórzanoetal2020; @Solórzanoetal2020]. If you want to add something inside the parentheses use comma [e.g., @Solórzanoetal2020].

# Methods

## Study site

Add |crop: true in the chunk to ignore white spaces around the figure. This is for figures made outside this document:

```{r fig1, echo= FALSE, warning=FALSE, message = FALSE,fig.width=16, fig.height=10, fig.cap = figure_f("Fig.1")}
#| crop: true

img <- image_read("D:/Drive/Jonathan_trabaggio/Doctorado/R/CometaLiDARrevML/Map/Map1.jpeg")
img |> 
  grid::grid.raster()
```

## Data

### Sampling method

Use superscripts and subscript $m^2$ and $x_i$
Reference equations @eq:eqn1: Double money sign is for equation in its own line

$$x = y$${#eq:eqn1}

greek letters $\rho$, italics: *Zygia recordii* and bold **Cactaceae**

more complex equations:

$$RMSE = \sqrt{\sum_{i=1}^{n} \frac{(\hat{y}_i - y_i)}{n}}$$ {#eq:eqn2}

where $\hat{y}$ stands for the predicted AGB value and $y$ for the
observed AGB value of each plot ($i$); while $n$ stands for the number
of sampled plots. 

# Results

## Field data

In line code can be used as: 
`r round(mean(df$AGB), 2)` Mg/ha 

This is for images built in the document:

```{r fig2, echo= FALSE, warning=FALSE, message = FALSE,fig.width=16, fig.height=10, fig.cap = figure_f("Fig. 2")}
#| crop: true
df_compl |>
  ggplot(aes(x = SumaAGB_ha, 
             y = SumaAGB_ha,
             col = as.factor(Sitio), 
             ymin = IC2.5,
             ymax = IC97.5)) + 
  geom_point(show.legend = FALSE,
             size = 2,
             position=position_dodge(width=0.5)) +
  geom_errorbar(show.legend = FALSE,
                lwd = 1,
                position=position_dodge(width=0.5)) +
  scale_x_continuous(expand = c(0,0)) +
  scale_y_continuous(expand = c(0,0)) +
  labs(x = "AGB (Mg/ha)", 
       y = "AGB (Mg/ha)") + 
  cowplot::theme_cowplot() + 
  theme(
    text=element_text(size=20,colour="black"),
    axis.text = element_text(size=20, colour="black", angle = 90, hjust = 1, vjust = 0.5), 
    axis.title = element_text(size=20, colour="black", face = "bold"), axis.line = element_line(colour = "black"))
```
For tables, use flextable

Remember each chunk should have its unique name.

```{r tablemodels, echo= FALSE}
tab2 <- tibble()

flextable(tab2) |>  
  set_header_labels(model = "Model", 
    var1 = "Var 1", 
    var2 = "Var 2", 
    var3 = "Var 3",
    rmse_train = "RMSE train",
    rmse_test = "RMSE test",
    rrmse_train = "RMSE train (%)",
    rrmse_test = "RMSE test (%)",
    r2_train = "R2 train",
    r2_test = "R2 test") |>
  colformat_double() |>
  # Custom titles
  flextable::compose(part = "header", i = 1, j = c(9, 10),
         value = c(as_paragraph(as_i("R"),
                              as_i(as_sup("2")),
                              " train"),
                   as_paragraph(as_i("R"),
                              as_i(as_sup("2")),
                              " test"))) |>
  set_caption(
    as_paragraph(
      as_chunk(table_f("Tab1"))
    ), word_stylename = "Table Caption"
  ) %>%
  set_table_properties(layout = "autofit")

```

# Conclusion

# References
